Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-11 analysis/paper/paper.Rmd
Last edit for the night. Code is in place, still need to write up my analysis. Trying to weed out bugs.

```
```{r}
# here we import the CSV file of caliper measurements, then compute on the
# measurements to generate coordinates for a shape outline

@@

# take a look to ensure we are on the right track
p <- ggplot() +
  geom_polygon(data=polys,
               aes(x=x,
                   y=y,
                   group = fill),
               colour="black",
               alpha = 0.5) +
  coord_equal() +
  theme_bw()
p

@@

```
```{r}
ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  mutate(dorsal_cortext_group = as.factor(
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 50) ~ "Secondary",
             between(dorsal_cortex_perc, 51, 100) ~ "Primary"
           ))) %>% 
 mutate(mass_group = as.factor(test_result_mass$cluster))
# plot mass groups
ggplot(ma_flakes_tr_with_groups)  +
  aes(mass,
      fill = mass_group) +
  geom_histogram() +
  scale_fill_viridis_d(name = "Mass\ncluster") +
  xlab("Mass (g)") +
  theme_minimal(base_size = 14) +
  theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
        plot.background = element_rect(fill='white',
                                       colour = "white"))

>>>>

```{r}
# here we import the CSV file of caliper measurements, then compute on the
# measurements to generate coordinates for a shape outline

@@

@@

<!--(11 Feb 2022) QH: Currently it is 1:20 AM. I have been fiddling about with code and github for awhile. I plan on fixing everything when I wake up, and, failing that, Friday afternoon.-->
```{r}
ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  mutate(dorsal_cortext_group = as.factor(
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 50) ~ "Secondary",
             between(dorsal_cortex_perc, 51, 100) ~ "Primary"
           ))) #%>% 
 #QH here, not sure what this is doing for now, just putting it off to the side: mutate(mass_group = as.factor(test_result_mass$cluster))
# plot mass groups
ggplot(ma_flakes_tr_with_groups)  +
  aes(mass,
      fill = mass_group) +
  geom_histogram() +
  scale_fill_viridis_d(name = "Mass\ncluster") +
  xlab("Mass (g)") +
  theme_minimal(base_size = 14) +
  theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
        plot.background = element_rect(fill='white',
                                       colour = "white"))
